Moral Foundations of U.S. Political News Organizations

### 2023-09-01 manuscript_version/revision/manuscript_metapsych_revision.Rmd
updating with irb

```{r load_packages, include = FALSE}
library(papaja)
library(MuMIn)
library(reshape)
library(nlme)
library(ggplot2)
library(expss)
library(MOTE)
library(quanteda)
library(quanteda.textstats)
library(tm)
library(ngram)
library(ggplot2)
library(reshape)
library(knitr)
library(performance)
library(dplyr)
library(rio)

@@

A complete example of the survey can be found online at OSF LINK. First, participants were given a description of associative memory as the relation between words that comes about through many pairings in writing and speech. Next, the free association task, similar to that used in @Nelson2004 and @SWOW_FIX_THIS was described to the participants as listing the "first word that pops into mind". The participants were then given three example free association cues, *lost*, *old*, and *article*. For each cue, participants were asked to write all the words that come to mind. To elicit free association to the moral foundation areas, participants were given the following instructions:

@@

All data was screening for inaccurate responses, as well as missing data, as described in the participant section. Two participants were missing data on the political orientation scale after excluding participants with more than five percent missing data, and this data was excluded pairwise. The MFQ data was screened for multivariate outliers with Mahalanobis distance as described in @Tabachnick2012, and fourteen outliers were found using $\chi^2_{p < .001}$(`r ncol(finalsample[ , -c(1:6,22,23)])`) = `r cutoff1`. These participants were excluded from further analyses, representing `r nrow(noout1)` final participants. The final data was screened for assumptions of normality, linearity, homogeneity and homoscedasticity, and these were found to be satisfactory.

The sum of each moral foundation area was calculated in order to determine which words were linked to their respective moral foundation. The average scores were: harm (*M* = `r printnum(mean(noout1$harmMFQ))`, *SD* = `r printnum(sd(noout1$harmMFQ))`), fairness  (*M* = `r printnum(mean(noout1$fairMFQ))`, *SD* = `r printnum(sd(noout1$fairMFQ))`), ingroup (*M* = `r printnum(mean(noout1$ingroupMFQ))`, *SD* = `r printnum(sd(noout1$ingroupMFQ))`), authority  (*M* = `r printnum(mean(noout1$authorityMFQ))`, *SD* = `r printnum(sd(noout1$authorityMFQ))`), and purity (*M* = `r printnum(mean(noout1$purityMFQ))`, *SD* = `r printnum(sd(noout1$purityMFQ))`). Participants free association responses were processed using the *tm* library [@CITE] after spell checking. Each set of answers was cleaned for punctuation, English stop words (e.g., *the*, *an*, *of*) were removed, and each word was stemmed using the English library in *tm*. We did not combine related words in this section (i.e., *injure* and *injury*, which have different stems *injur* and *injuri*) to allow for maximum coverage of different word forms present in the dictionary. Additionally, with the use of automated stemmers like that present in the *tm* library, leaving both word forms in the dictionary would capture more of the concepts present in future analyses with a different corpus without the requirement on the experimenter to manuall recode all word forms. Frequency counts of the stemmed words were tabulated and only words mentioned with at least one percent frequency were used in the subsequent analyses. The complete set of word frequencies for each foundation can be found in our supplemental materials.

```{r harm-analysis-3.1, include = FALSE}
#q27 through 34 are the writing columns
noout1$Q27 = as.character(noout1$Q27)

##stem the data

for (i in 1:nrow(noout1)) {
  noout1$Q27[i] = paste(unlist(
    text_tokens(noout1$Q27[i], stemmer = "en")), collapse = " ")
}

##create a corpus
harm_corpus = Corpus(VectorSource(noout1$Q27))
harm_TDM = as.matrix(TermDocumentMatrix(harm_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
harm_freq = data.frame(Word = rownames(harm_TDM),
                       Freq = rowSums(harm_TDM),
                       row.names = NULL)
harm_freq$Word = as.character(harm_freq$Word)
harm_freq$percent = harm_freq$Freq/nrow(noout1) *100

write.csv(harm_freq, "exp1_harm_freq.csv", row.names = F)

##subset out to only words with 1% mentions
harm_words = harm_freq$Word[harm_freq$percent >=1]
##turn sideways to add to dataset
harm_TDM = as.data.frame(t(harm_TDM))
harm_TDM = harm_TDM[ , harm_words]

##final dataset for harm
harm_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "harmMFQ")],
                   harm_TDM)

harm_cor = apply(harm_final[ , 5:ncol(harm_final)], 2, function (x) { cor(x, harm_final$harmMFQ)})

harmcut = mean(harm_cor) + 2*sd(harm_cor)
harm_words_reduce = names(harm_cor[abs(harm_cor) >= harmcut])
```

@@

##stem the data
for (i in 1:nrow(noout1)) {
  noout1$Q29[i] = paste(unlist(
    text_tokens(noout1$Q29[i], stemmer = "en")), collapse = " ")
}

##create a corpus
fair_corpus = Corpus(VectorSource(noout1$Q29))
fair_TDM = as.matrix(TermDocumentMatrix(fair_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
fair_freq = data.frame(Word = rownames(fair_TDM),
                       Freq = rowSums(fair_TDM),
                       row.names = NULL)
fair_freq$Word = as.character(fair_freq$Word)
fair_freq$percent = fair_freq$Freq/nrow(noout1) *100

write.csv(fair_freq, "exp1_fair_freq.csv", row.names = F)

##subset out to only words with 1% mentions
fair_words = fair_freq$Word[fair_freq$percent >=1]
##turn sideways to add to dataset
fair_TDM = as.data.frame(t(fair_TDM))
fair_TDM = fair_TDM[ , fair_words]

##final dataset for fair
fair_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "fairMFQ")],
                   fair_TDM)

fair_cor = apply(fair_final[ , 5:ncol(fair_final)], 2, function (x) { cor(x, fair_final$fairMFQ)})

faircut = mean(fair_cor) + 2*sd(fair_cor)
fair_words_reduce = names(fair_cor[abs(fair_cor) >= faircut])
```

```{r ingroup-analysis-3.1, include=FALSE}
#q27 through 34 are the writing columns
noout1$Q30 = as.character(noout1$Q30)

##stem the data
for (i in 1:nrow(noout1)) {
  noout1$Q30[i] = paste(unlist(
    text_tokens(noout1$Q30[i], stemmer = "en")), collapse = " ")
}

##create a corpus
ingroup_corpus = Corpus(VectorSource(noout1$Q30))
ingroup_TDM = as.matrix(TermDocumentMatrix(ingroup_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
ingroup_freq = data.frame(Word = rownames(ingroup_TDM),
                       Freq = rowSums(ingroup_TDM),
                       row.names = NULL)
ingroup_freq$Word = as.character(ingroup_freq$Word)
ingroup_freq$percent = ingroup_freq$Freq/nrow(noout1) *100

write.csv(ingroup_freq, "exp1_ingroup_freq.csv", row.names = F)

##subset out to only words with 1% mentions
ingroup_words = ingroup_freq$Word[ingroup_freq$percent >=1]
##turn sideways to add to dataset
ingroup_TDM = as.data.frame(t(ingroup_TDM))
ingroup_TDM = ingroup_TDM[ , ingroup_words]

##final dataset for ingroup
ingroup_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "ingroupMFQ")],
                   ingroup_TDM)

ingroup_cor = apply(ingroup_final[ , 5:ncol(ingroup_final)], 2, function (x) { cor(x, ingroup_final$ingroupMFQ)})

ingroupcut = mean(ingroup_cor) + 2*sd(ingroup_cor)
ingroup_words_reduce = names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
```

```{r authority-analysis-3.1, include = FALSE}
#q27 through 34 are the writing columns
noout1$Q32 = as.character(noout1$Q32)

##stem the data
for (i in 1:nrow(noout1)) {
  noout1$Q32[i] = paste(unlist(
    text_tokens(noout1$Q32[i], stemmer = "en")), collapse = " ")
}

##create a corpus
authority_corpus = Corpus(VectorSource(noout1$Q32))
authority_TDM = as.matrix(TermDocumentMatrix(authority_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
authority_freq = data.frame(Word = rownames(authority_TDM),
                       Freq = rowSums(authority_TDM),
                       row.names = NULL)
authority_freq$Word = as.character(authority_freq$Word)
authority_freq$percent = authority_freq$Freq/nrow(noout1) *100

write.csv(authority_freq, "exp1_authority_freq.csv", row.names = F)

##subset out to only words with 1% mentions
authority_words = authority_freq$Word[authority_freq$percent >=1]
##turn sideways to add to dataset
authority_TDM = as.data.frame(t(authority_TDM))
authority_TDM = authority_TDM[ , authority_words]

##final dataset for authority
authority_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "authorityMFQ")],
                   authority_TDM)

authority_cor = apply(authority_final[ , 5:ncol(authority_final)], 2, function (x) { cor(x, authority_final$authorityMFQ)})

authoritycut = mean(authority_cor) + 2*sd(authority_cor)
authority_words_reduce = names(authority_cor[abs(authority_cor) >= authoritycut])
```

```{r purity-analysis-3.1, include = FALSE}
#q27 through 34 are the writing columns
noout1$Q34 = as.character(noout1$Q34)

##stem the data
for (i in 1:nrow(noout1)) {
  noout1$Q34[i] = paste(unlist(
    text_tokens(noout1$Q34[i], stemmer = "en")), collapse = " ")
}

##create a corpus
purity_corpus = Corpus(VectorSource(noout1$Q34))
purity_TDM = as.matrix(TermDocumentMatrix(purity_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
purity_freq = data.frame(Word = rownames(purity_TDM),
                       Freq = rowSums(purity_TDM),
                       row.names = NULL)
purity_freq$Word = as.character(purity_freq$Word)
purity_freq$percent = purity_freq$Freq/nrow(noout1) *100

write.csv(purity_freq, "exp1_purity_freq.csv", row.names = F)

##subset out to only words with 1% mentions
purity_words = purity_freq$Word[purity_freq$percent >=1]
##turn sideways to add to dataset
purity_TDM = as.data.frame(t(purity_TDM))
purity_TDM = purity_TDM[ , purity_words]

##final dataset for purity
purity_final = cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "purityMFQ")],
                   purity_TDM)

purity_cor = apply(purity_final[ , 5:ncol(purity_final)], 2, function (x) { cor(x, purity_final$purityMFQ)})

puritycut = mean(purity_cor) + 2*sd(purity_cor)
purity_words_reduce = names(purity_cor[abs(purity_cor) >= puritycut])
```

This procedure generated a large frequency of words for a new dictionary of moral foundations: harm `r length(harm_words)`, fairness `r length(fair_words)`, ingroup `r length(ingroup_words)`, authority `r length(authority_words)`, and purity `r length(purity_words)`. These concepts were included in the full dictionary used for Experiment 3. We additionally created a reduced dictionary that included only concepts correlated with their respective moral foundations scores. Correlations between word frequency and the sum of the MFQ were calculated for each foundation and set of concepts. Words were included in the reduced dictionary if their correlation was two standard deviations away from the mean correlation for that foundation. The reduced dataset included the following number of words for each foundation: harm `r length(harm_words_reduce)`, fairness `r length(fair_words_reduce)`, ingroup `r length(ingroup_words_reduce)`, authority `r length(authority_words_reduce)`, and purity `r length(purity_words_reduce)`.

@@

```{r demos-mtmm-study-3.2, include=FALSE, warning=FALSE}
sample1 = read.csv("fixed_sample 1.csv", stringsAsFactors = F)
sample2 = read.csv("fixed_sample 2.csv", stringsAsFactors = F)

##merge files together
fullsample = merge(sample1, sample2, all = TRUE)

##merge together the writing samples
#q24, q25, q26, q7 
fullsample$writing = apply(fullsample[, c("Q24", "Q25", "Q26", "Q7")], 
                           1, function(x) toString(na.omit(x)))

##clear out completely columns we don't need
crapcolumns = c(1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 51:61)
finalsample = fullsample[ , -crapcolumns]

@@

finalsample$Q10 = factor(finalsample$Q10,
                         levels = 1:2,
                         labels = c("Man", "Woman"))
finalsample$Q11 = as.numeric(finalsample$Q11)
finalsample$Q12 = factor(finalsample$Q12,
                         levels = 1:7,
                         labels = c("White", "Black", 
                                    "Hispanic", "Asian",
                                    "Native American", 
                                    "Mixed", "Other"))

gender = table(finalsample$Q10)/sum(table(finalsample$Q10))*100
race = table(finalsample$Q12)/sum(table(finalsample$Q12))*100

write.csv(finalsample, 'exp2_finalsample.csv', row.names = FALSE)
newMFD = read.csv('exp2_finalsample_newMFD.csv')
colnames(newMFD)[1:41] = colnames(finalsample)[1:41]
newMFD = newMFD[,c(1,42:55)]
finalsample = merge(finalsample, newMFD, by="ResponseId")

@@

  finalsample$writing[i] = preprocess(finalsample$writing[i], case="lower", remove.punct=TRUE)
  finalsample$wordcount[i] = string.summary(finalsample$writing[i])$words

@@

#remove small words people
finalwords = subset(finalsample, wordcount >=25)

##check out missing data
#missing by row
missing = apply(finalwords, 1, percentmiss)
table(missing)
goodrows = subset(finalwords, missing <= 5)

@@

##don't fill in Q10 to the end, be sure to merge these back together
goodcolumns = goodrows[ , -c(32:42)]
badcolumns = goodrows[ , c(32:42)]

#fill in missing data points
library(mice)
tempnomiss = mice(goodcolumns)
nomiss = complete(tempnomiss, 1)
summary(nomiss)
#merge
allcolumns = cbind(nomiss, badcolumns) 
summary(allcolumns)

>>>>

```{r load_packages, include = FALSE}
library(papaja)
library(MuMIn)
library(reshape)
library(nlme)
library(ggplot2)
library(expss)
library(MOTE)
library(quanteda)
library(quanteda.textstats)
library(tm)
library(ngram)
library(ggplot2)
library(reshape)
library(knitr)
library(performance)
library(dplyr)
library(rio)
library(mice)

# to install this package 
# tmp <- tempfile()
# system2("git", c("clone", "--recursive",
#                  shQuote("https://github.com/leslie-huang/r-corpus.git"), shQuote(tmp)))
# devtools::install(tmp)
library(corpus)

@@

A complete example of the survey can be found online at https://osf.io/5uqfn. First, participants were given a description of associative memory as the relation between words that comes about through many pairings in writing and speech. Next, the free association task, similar to that used in CITE @Nelson2004 and @SWOW_FIX_THIS was described to the participants as listing the "first word that pops into mind". The participants were then given three example free association cues, *lost*, *old*, and *article*. For each cue, participants were asked to write all the words that come to mind. To elicit free association to the moral foundation areas, participants were given the following instructions:

@@

All data was screening for inaccurate responses, as well as missing data, as described in the participant section. Two participants were missing data on the political orientation scale after excluding participants with more than five percent missing data, and this data was excluded pairwise. The MFQ data was screened for multivariate outliers with Mahalanobis distance as described in @Tabachnick2012 CITE, and fourteen outliers were found using $\chi^2_{p < .001}$(`r ncol(finalsample[ , -c(1:6,22,23)])`) = `r apa_num(cutoff1)`. These participants were excluded from further analyses, representing `r nrow(noout1)` final participants. The final MFQ data was screened for assumptions of normality, linearity, homogeneity and homoscedasticity, and these were found to be satisfactory.

The sum of each moral foundation area was calculated in order to determine which words were linked to their respective moral foundation. The average scores were: harm (*M* = `r printnum(mean(noout1$harmMFQ))`, *SD* = `r printnum(sd(noout1$harmMFQ))`), fairness  (*M* = `r printnum(mean(noout1$fairMFQ))`, *SD* = `r printnum(sd(noout1$fairMFQ))`), ingroup (*M* = `r printnum(mean(noout1$ingroupMFQ))`, *SD* = `r printnum(sd(noout1$ingroupMFQ))`), authority  (*M* = `r printnum(mean(noout1$authorityMFQ))`, *SD* = `r printnum(sd(noout1$authorityMFQ))`), and purity (*M* = `r printnum(mean(noout1$purityMFQ))`, *SD* = `r printnum(sd(noout1$purityMFQ))`). Participants free association responses were processed using the *tm* [CITE] and *corpus* [CITE] libraries after spell checking. Each set of answers was cleaned for punctuation, English stop words (e.g., *the*, *an*, *of*) were removed, and each word was stemmed using the English library in *tm*. We did not combine related words in this section (i.e., *injure* and *injury*, which have different stems *injur* and *injuri*) to allow for maximum coverage of different word forms present in the dictionary. Additionally, with the use of automated stemmers like that present in the *tm* library, leaving both word forms in the dictionary would capture more of the concepts present in future analyses with a different corpus without the requirement on the experimenter to manually recode all word forms. Frequency counts of the stemmed words were tabulated and only words mentioned with at least one percent frequency were used in the subsequent analyses. The complete set of word frequencies for each foundation can be found in our supplemental materials.

```{r harm-analysis-3.1, include = FALSE}
#q27 through 34 are the writing columns
noout1$Q27 <- as.character(noout1$Q27)

##stem the data
for (i in 1:nrow(noout1)) {
  noout1$Q27[i] <- paste(unlist(
    text_tokens(noout1$Q27[i], stemmer = "en")), collapse = " ")
}

##create a corpus
harm_corpus <- Corpus(VectorSource(noout1$Q27))
harm_TDM <- as.matrix(TermDocumentMatrix(harm_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
harm_freq <- data.frame(Word = rownames(harm_TDM),
                       Freq = rowSums(harm_TDM),
                       row.names = NULL)
harm_freq$Word <- as.character(harm_freq$Word)
harm_freq$percent <- harm_freq$Freq/nrow(noout1) *100

write.csv(harm_freq, "exp3_data/study3.1_harm_freq.csv", row.names = F)

##subset out to only words with 1% mentions
harm_words <- harm_freq$Word[harm_freq$percent >=1]
##turn sideways to add to dataset
harm_TDM  <- as.data.frame(t(harm_TDM))
harm_TDM  <- harm_TDM[ , harm_words]

##final dataset for harm
harm_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "harmMFQ")],
                   harm_TDM)

harm_cor <- apply(harm_final[ , 5:ncol(harm_final)], 2, function (x) { cor(x, harm_final$harmMFQ)})

harmcut <- mean(harm_cor) + 2*sd(harm_cor)
harm_words_reduce <- names(harm_cor[abs(harm_cor) >= harmcut])
```

@@

##stem the data
for (i in 1:nrow(noout1)) {
  noout1$Q29[i] <- paste(unlist(
    text_tokens(noout1$Q29[i], stemmer = "en")), collapse = " ")
}

##create a corpus
fair_corpus <- Corpus(VectorSource(noout1$Q29))
fair_TDM <- as.matrix(TermDocumentMatrix(fair_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
fair_freq <- data.frame(Word = rownames(fair_TDM),
                       Freq = rowSums(fair_TDM),
                       row.names = NULL)
fair_freq$Word <- as.character(fair_freq$Word)
fair_freq$percent <- fair_freq$Freq/nrow(noout1) *100

write.csv(fair_freq, "exp3_data/study3.1_fair_freq.csv", row.names = F)

##subset out to only words with 1% mentions
fair_words <- fair_freq$Word[fair_freq$percent >=1]
##turn sideways to add to dataset
fair_TDM <- as.data.frame(t(fair_TDM))
fair_TDM <- fair_TDM[ , fair_words]

##final dataset for fair
fair_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "fairMFQ")],
                   fair_TDM)

fair_cor <- apply(fair_final[ , 5:ncol(fair_final)], 2, function (x) { cor(x, fair_final$fairMFQ)})

faircut <- mean(fair_cor) + 2*sd(fair_cor)
fair_words_reduce <- names(fair_cor[abs(fair_cor) >= faircut])
```

```{r ingroup-analysis-3.1, include=FALSE}
#q27 through 34 are the writing columns
noout1$Q30 <- as.character(noout1$Q30)

##stem the data
for (i in 1:nrow(noout1)) {
  noout1$Q30[i] <- paste(unlist(
    text_tokens(noout1$Q30[i], stemmer = "en")), collapse = " ")
}

##create a corpus
ingroup_corpus <- Corpus(VectorSource(noout1$Q30))
ingroup_TDM <- as.matrix(TermDocumentMatrix(ingroup_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
ingroup_freq <- data.frame(Word = rownames(ingroup_TDM),
                       Freq = rowSums(ingroup_TDM),
                       row.names = NULL)
ingroup_freq$Word <- as.character(ingroup_freq$Word)
ingroup_freq$percent <- ingroup_freq$Freq/nrow(noout1) *100

write.csv(ingroup_freq, "exp3_data/study3.1_ingroup_freq.csv", row.names = F)

##subset out to only words with 1% mentions
ingroup_words <- ingroup_freq$Word[ingroup_freq$percent >=1]
##turn sideways to add to dataset
ingroup_TDM <- as.data.frame(t(ingroup_TDM))
ingroup_TDM <- ingroup_TDM[ , ingroup_words]

##final dataset for ingroup
ingroup_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "ingroupMFQ")],
                   ingroup_TDM)

ingroup_cor <- apply(ingroup_final[ , 5:ncol(ingroup_final)], 2, function (x) { cor(x, ingroup_final$ingroupMFQ)})

ingroupcut <- mean(ingroup_cor) + 2*sd(ingroup_cor)
ingroup_words_reduce <- names(ingroup_cor[abs(ingroup_cor) >= ingroupcut])
```

```{r authority-analysis-3.1, include = FALSE}
#q27 through 34 are the writing columns
noout1$Q32 <- as.character(noout1$Q32)

##stem the data
for (i in 1:nrow(noout1)) {
  noout1$Q32[i] <- paste(unlist(
    text_tokens(noout1$Q32[i], stemmer = "en")), collapse = " ")
}

##create a corpus
authority_corpus <- Corpus(VectorSource(noout1$Q32))
authority_TDM <- as.matrix(TermDocumentMatrix(authority_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
authority_freq <- data.frame(Word = rownames(authority_TDM),
                       Freq = rowSums(authority_TDM),
                       row.names = NULL)
authority_freq$Word <- as.character(authority_freq$Word)
authority_freq$percent <- authority_freq$Freq/nrow(noout1) *100

write.csv(authority_freq, "exp3_data/study3.1_authority_freq.csv", row.names = F)

##subset out to only words with 1% mentions
authority_words <- authority_freq$Word[authority_freq$percent >=1]
##turn sideways to add to dataset
authority_TDM <- as.data.frame(t(authority_TDM))
authority_TDM <- authority_TDM[ , authority_words]

##final dataset for authority
authority_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "authorityMFQ")],
                   authority_TDM)

authority_cor <- apply(authority_final[ , 5:ncol(authority_final)], 2, function (x) { cor(x, authority_final$authorityMFQ)})

authoritycut <- mean(authority_cor) + 2*sd(authority_cor)
authority_words_reduce <- names(authority_cor[abs(authority_cor) >= authoritycut])
```

```{r purity-analysis-3.1, include = FALSE}
#q27 through 34 are the writing columns
noout1$Q34 <- as.character(noout1$Q34)

##stem the data
for (i in 1:nrow(noout1)) {
  noout1$Q34[i] <- paste(unlist(
    text_tokens(noout1$Q34[i], stemmer = "en")), collapse = " ")
}

##create a corpus
purity_corpus <- Corpus(VectorSource(noout1$Q34))
purity_TDM <- as.matrix(TermDocumentMatrix(purity_corpus,
                              control = list(removePunctuation = TRUE,
                                             stopwords = TRUE)))

##view the most frequent words
purity_freq <- data.frame(Word = rownames(purity_TDM),
                       Freq = rowSums(purity_TDM),
                       row.names = NULL)
purity_freq$Word <- as.character(purity_freq$Word)
purity_freq$percent <- purity_freq$Freq/nrow(noout1) *100

write.csv(purity_freq, "exp3_data/study3.1_purity_freq.csv", row.names = F)

##subset out to only words with 1% mentions
purity_words <- purity_freq$Word[purity_freq$percent >=1]
##turn sideways to add to dataset
purity_TDM <- as.data.frame(t(purity_TDM))
purity_TDM <- purity_TDM[ , purity_words]

##final dataset for purity
purity_final <- cbind(noout1[ , c("ResponseId", "Q15_1", "Q23", "purityMFQ")],
                   purity_TDM)

purity_cor <- apply(purity_final[ , 5:ncol(purity_final)], 2, function (x) { cor(x, purity_final$purityMFQ)})

puritycut <- mean(purity_cor) + 2*sd(purity_cor)
purity_words_reduce <- names(purity_cor[abs(purity_cor) >= puritycut])
```

This procedure generated a large frequency of words for a new dictionary of moral foundations: harm `r length(harm_words)`, fairness `r length(fair_words)`, ingroup `r length(ingroup_words)`, authority `r length(authority_words)`, and purity `r length(purity_words)`. These concepts were included in the full dictionary used for Study 3.3. We additionally created a reduced dictionary that included only concepts correlated with their respective moral foundations scores. Correlations between word frequency and the sum of the MFQ were calculated for each foundation and set of concepts. Words were included in the reduced dictionary if their correlation was two standard deviations away from the mean correlation for that foundation. The reduced dataset included the following number of words for each foundation: harm `r length(harm_words_reduce)`, fairness `r length(fair_words_reduce)`, ingroup `r length(ingroup_words_reduce)`, authority `r length(authority_words_reduce)`, and purity `r length(purity_words_reduce)`.

@@

```{r demos-mtmm-study-3.2, include=FALSE, warning=FALSE}
sample1 <- read.csv("exp3_data/study3.2_fixed_sample 1.csv", stringsAsFactors = F)
sample2 <- read.csv("exp3_data/study3.2_fixed_sample 2.csv", stringsAsFactors = F)

##merge files together
fullsample <- merge(sample1, sample2, all = TRUE)

##merge together the writing samples
#q24, q25, q26, q7 
fullsample$writing <- apply(fullsample[, c("Q24", "Q25", "Q26", "Q7")], 
                           1, function(x) toString(na.omit(x)))

##clear out completely columns we don't need
crapcolumns <- c(1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 51:61)
finalsample <- fullsample[ , -crapcolumns]

@@

finalsample$Q10 <- factor(finalsample$Q10,
                         levels = 1:2,
                         labels = c("Man", "Woman"))
finalsample$Q11 <- as.numeric(finalsample$Q11)
finalsample$Q12 <- factor(finalsample$Q12,
                         levels = 1:7,
                         labels = c("White", "Black", 
                                    "Hispanic", "Asian",
                                    "Native American", 
                                    "Mixed", "Other"))

gender <- table(finalsample$Q10)/sum(table(finalsample$Q10))*100
race <- table(finalsample$Q12)/sum(table(finalsample$Q12))*100

write.csv(finalsample, 'exp3_data/study3.2_finalsample.csv', row.names = FALSE)
newMFD <- import('exp3_data/study3.2_finalsample_newMFD.csv')
colnames(newMFD)[1:41] <- colnames(finalsample)[1:41]
newMFD <- newMFD[,c(1,42:55)]
finalsample <- merge(finalsample, newMFD, by = "ResponseId")

@@

  finalsample$writing[i] <- preprocess(finalsample$writing[i], case="lower", remove.punct=TRUE)
  finalsample$wordcount[i] <- string.summary(finalsample$writing[i])$words

@@

#remove small words people
finalwords <- subset(finalsample, wordcount >=25)

##check out missing data
#missing by row
missing <- apply(finalwords, 1, percentmiss)
table(missing)
goodrows <- subset(finalwords, missing <= 5)

@@

##don't fill in Q10 to the end, be sure to merge these back together
goodcolumns <- goodrows[ , -c(32:42)]
badcolumns <- goodrows[ , c(32:42)]

#fill in missing data points

tempnomiss = mice(goodcolumns)
nomiss = complete(tempnomiss, 1)
summary(nomiss)
#merge
allcolumns = cbind(nomiss, badcolumns) 
summary(allcolumns)
